Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-04 manuscript-chicago.Rmd
Add references to approx. figure and table locations

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

[Figure \@ref(fig:cohesion-in-tweets) about here]

@@

[Figure \@ref(fig:theoretical-framework) about here]

@@

[Figure \@ref(fig:raw-cohesion-ts) about here]

@@

```
[Figures \@ref(fig:raw-event-ts-target) and \@ref(fig:raw-event-ts-source-target) about here]

@@

[Figures \@ref(fig:raw-ts) and \@ref(fig:deciled-ts) about here]

@@

[Figure \@ref(fig:plot-rp-targ) and \autoref{table-1} about here]

@@

[Figure \@ref(fig:plot-rp-source-targ) and \autoref{table-2} about here]

@@

[Figure \@ref(fig:plot-wcrqa-targ-all) about here]

@@

[Figure \@ref(fig:plot-wcrqa-source-targ-all) about here]

@@

[Figure \@ref(fig:plot-mode-event) about here]
